Multi-line Intensity Mapping

### 2019-06-24 paper/ms.tex
Add cross-spectrum
Finish of multi-line formalism section

@@

>>>>

\newcommand{\bi}{\ensuremath{\avg{b_i}}}
\newcommand{\bj}{\ensuremath{\avg{b_j}}}
\newcommand{\Ii}{\ensuremath{\avg{I_i}}}
\newcommand{\Ij}{\ensuremath{\avg{I_j}}}

@@

For the cross-spectrum between two lines $i$ and $j$, we assume that {\bf need
to fix this with the shot noise component}
\beq\label{eq:cross_spec}
P_{i,j}(k, \mu, z) = r_{i,j}(k, z) \sqrt{P_{i,i}(k, \mu, z) P_{j,j}(k, \mu, z)}
\eeq

\subsection{Multi-line Formalism}\label{ssec:multi_line}
Given a set of cross-spectra and their covariance matrix, we can determine the
optimal constraints that can be placed on both the average bias $\avg{b_i}$
and average intensity $\avg{I_i}$. For the set of parameters $\theta$
containing each $\avg{b_i}$ and $\avg{I_i}$, we can write down the Fisher
matrix as
\beq\label{eq:fisher}
F_{i,j} = 
\int \frac{\text{d}^3k}{(2\pi)^3} V_{\text{surv}}
% \int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
\sum_{l} \sum_{m}
\frac{\partial \hat{P}_{l}(\bm{k})}{\partial \theta_i}
\left(\Cov{\hat{P}_{l}(\bm{k})}{\hat{P}_{m}(\bm{k})}\right)^{-1}
\frac{\partial \hat{P}_{m}(\bm{k})}{\partial \theta_j}\text{,}
\eeq
where the sum over $l$ and $m$ each is over each \emph{pair} of lines.

While in principle one can extract $\bi$ and $\Ii$ independently due to the
$\mu$-dependence of the Kaiser effect, there are a number of observational
challenges {\bf Dongwoo 2019}. We will therefore only consider the constraints
that can be placed on the product of the two, i.e., $B_i \equiv \bi \Ii$. The
previous Fisher matrix can be converted to the equivalent one for constraints
on $B_i$, $F'$, by the following relation (e.g. {\bf Coe 2009}):
\beq\label{eq:fisher_transform}
F' = M^{\mathsf{T}} F M\text{,}
\eeq
where
\beq\label{eq:trans_matrix}
M_{ij} = \frac{\partial \theta_i}{\partial B_j}\text{.}
\eeq
